\section*{Introduction}
\label{sec:intro}
Many research has revealed that analyzing tweets in volume can measure different population characteristics, including public
health measures \cite{paul2011you, paul2012model, eichstaedt2015psychological, barros2018disease, mueller2018crowdbreaks, karami2018characterizing}.
Research analysis like correlating influenza rates w.r.t geography (spatial) and time \cite{signorini2011use}, state level food and health behavior analysis \cite{nguyen2017social}, predicting heart disease rate mortality rate based on twitter information \cite{eichstaedt2015psychological}; are motivating examples to carry out such analysis for improving and create for public health.
All these above adhoc analysis motivates to build a general system for comprehensive analysis.
In this work, I will present overview of architechture and desired features to build such system or tools.




Machine Learning  +  Data Processing

gathering data

bot detection - remove bias

% Predicting User Location:(only 0.85\% tweets geotagged) http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.699.8571&rep=rep1&type=pdf

42\% tweets photos. and photos contain more information . (utilize it)

classification

sentiment (happy or sad)

user-characteristic:

% Model for ailment: (https://www.aaai.org/ocs/index.php/ICWSM/ICWSM11/paper/viewFile/2880/3264)
Heart disease mortality rate based on twitter. (see resources)

Predict relation with food and health habits with user tweets. (The Ugly Controversial analysis: Opinion about individual (dangerous))
  Disease mention for
  in airport and hospital geolocations expose dominance of news events for disease concerns
  https://jbiomedsem.biomedcentral.com/articles/10.1186/s13326-018-0186-9
  Does that mean people travelling more are in risk more? Health insurance?


Realtime data processing:  (AI Pro)

Online Query processing:
  spatial indexing - spatial query support simba
  integrating spatial indexing with time.
  Online join- wanderjoin - estimarors - confidence intervals. (how happy people  are in region X ).
  unbiased sampling

  Analysis on time of the day  (when people tweet what?) i.e. adding index level with spatio-temporal


More features:
multi-lingual models.


% Resources:
% https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0103408



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
